Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
another pass

Obtaining good sets of JS test cases is imperative to evaluate the
techniques in this paper. For that, we looked for \js\ files from
various sources: 1) test files from the Test262~\cite{tc39-github}
conformance suite of the ECMA262 specification~\cite{ecmas262-spec},
2) test files from the test suite of our selected engines; these files
are accessible from the engine's official repositories, 3) test files
from the suites of other public engines (\ie{}, Duktape, JerryScript,
JSI, and Tiny-js), 4) test files mined from issue trackers of these
engines, and 5) test files from other GitHub projects.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' shows the tests used for
    test transplantation whereas the rectangle under column
    ``no-fail-in-all''---a subset of the ``type-in-all'' tests---shows
    the tests used in cross-engine differential
    testing.}
  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
    \midrule
    \jsc & \cite{jsc2018repo} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
    \veight{} & \cite{v82018repo} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
    %\chakra & \cite{chakra2018repo}\\
    %\hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
    \midrule
    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\
    \jerry{} & \cite{jerryscript2018repo} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
    \midrule
    %GitHub Projects & - & 494,394 & - & - & - \\
    %\midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule
  \end{tabular}
\end{table}

Table~\ref{tab:test-suites} shows the breakdown of tests. Column
``Name'' and ``Source'' show the origin of the test suite. Column
``total'' shows the number of test cases associated with a givem
source. Column ``pass-in-par.''  shows the number of test cases that
pass in their parent engine. We discarded tests that fail in their
parent engine as we could not reliably indicate the reason for the
failure, so we assumed the test could be broken. We removed
\testsThatFail{} test cases that fail for that
reason--\testsThatFailJSC{} tests from \jsc and \testsThatFailSM{}
tests from \smonkey. Column ``type-in-all'' shows the number of test
cases whose executions do not throw dynamic type errors in any of the
engines because of an undefined variable or property.  These cases
were captured by looking for the presence of \CodeIn{ReferenceError}
and \CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. Similarly, the \chakra project does not use
  the default well-known assertions available in JS, which the other
  JS engines use.  Instead, it uses its own testing framework,
  WScript. In this case, we could not easily reproduce the \chakra
  unit tests in the other engines since it would raise a
  \texttt{ReferenceError}. Also, updating the other engines to use
  WScript would require a non-trivial manual effort. This is why
  \chakra does not appear in Table~\ref{tab:test-suites}.

@@

\subsection{Mining Tests}

To enrich our dataset of test files, we mined additional tests available on
JavaScript GitHub projects as well as in the issue trackers of the studied
JS engines. We explain this process next.

\subsubsection{From GitHub projects}

We mined JS programs from the GitHub repository. In this case, we searched
for projects written in JavaScript, that were tagged with ``javascript-engine",
and that have both ``Javascript" and ``engine" the name or the description of
the project. After this process, we ended up with 2,200 JS programs, which we
downloaded locally. However, after careful investigation, we noted that 160 of
these projects do not have any JS file, which were excluded from our study.
From these 2,040 projects, we could select 494,394 test files,
which we as input to our testing approaches.

\subsubsection{From Issue Trackers}

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:cross-testing}Number of failures with
    Test Transplantation.}
  \renewcommand*{\arraystretch}{0.9}
  \begin{tabular}{crrrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc & \veight{} & \smonkey{} & \chakra{} & \hermes{} \\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0
      JSC 2
      Spidermonkey 58
    }
    \jsc & - & 10 & 10 & 59 & 340  \\
    \veight{} & 41 & - & 3 & 5 & 315 \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 281 & - \\
    Hermes & 8 & 14 & 8 & 26 & -  \\
    Duktape & 0 & 4 & 4 & 1 & 140  \\
    \jerry{} & 23 & 25 & 22 & 23 & 311  \\
    JSI & 0 & 0 & 0 & 0 & 40\\
   Tiny-js & 0 & 0 & 0 & 0 & 10  \\
    \midrule
   \textbf{total} & 290 & 160 & 47 & 395 & 1156 \\
    \bottomrule
  \end{tabular}
  \vspace{-3ex}
\end{table}

@@

Table~\ref{tab:cross-testing} shows the number of failures observed
for each pair of test suite and engine. The first column shows the
test suites and the first row shows the engines that run those
tests. We use a dash (``-'') to indicate that we did not consider the
combinations that associate a test suite with its parent engine.
\Fix{
In particular, we were not able to reuse the \smonkey tests on the
\hermes engine. This happened because \smonkey has its own assertion
framework, but \hermes did not interpret these assertions, resulting
in failures in all test executions from this engine. These failures
did not happen when the \smonkey tests were transplanted to the other engines,
though.
}
failures in those cases would either indicate regressions or flaky
tests as opposed to unknown bugs for that engine. As explained in
Section~\ref{sec:seeds}, we used in this experiment the
\totalTestFilesForTestTransplantation{} tests included in the
rectangle area under column ``type-in-all'' from
Table~\ref{tab:test-suites}. Running those tests we observed a total
of \failuresTestTrans{} failures manifested across
\failuresTestTransDistictFiles{} distinct files
(\failuresTestTransPercent{} of total).  Table~\ref{tab:cross-testing}
shows that \smonkey\ was the engine that failed the least whereas
\chakra\ was the engine that failed the most. The \smonkey\ test suite
also revealed more failures than any other, as expected, given
that it is the suite with more tests (see
Table~\ref{tab:test-suites}).

@@

\sloppy The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc defines a function with a tail-call
recursion. The test fails in all engines but \jsc, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} did not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}.
\textbf{Non-Standard Element.} These cases manifest when a function or
an object property is undefined in the execution engine but we were
unable to capture that by looking for error types like
\CodeIn{ReferenceError} and \CodeIn{TypeError}.\Comment{ For example,
  we found cases where the test (or its harness) fails in an assertion
  because of an undefined property.}  \textbf{Other.} This category
includes other sources of false positives. For example, it includes
the cases where the test was valid for some previous version of the
spec but is no longer valid for the current spec.

>>>>

Obtaining good sets of JS test cases is imperative to evaluate the
techniques in this paper. For that, we looked for \js\ files from
various sources: 1) test files from the Test262~\cite{tc39-github}
conformance suite of the ECMA262 specification~\cite{ecmas262-spec},
2) test files from the test suite of our selected engines; these files
are accessible from the engine's official repositories, 3) test files
from the suites of other public engines (\ie{}, Duktape, JerryScript,
JSI, Tiny-js, Babel, and BlogEngine.NET),
and 4) test files mined from issue trackers of these
engines.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' shows the tests used for
    test transplantation whereas the rectangle under column
    ``no-fail-in-all''---a subset of the ``type-in-all'' tests---shows
    the tests used in cross-engine differential
    testing.}
  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
    \midrule
    \jsc & \cite{jsc2018repo} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
    \veight{} & \cite{v82018repo} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
    %\chakra & \cite{chakra2018repo}\\
    \hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
    \midrule
    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\
    \jerry{} & \cite{jerryscript2018repo} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
    Babel &&&&& \\
    BlogEngine.NET &&&&& \\
    \midrule
    %GitHub Projects & - & 494,394 & - & - & - \\
    %\midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule
  \end{tabular}
\end{table}

Table~\ref{tab:test-suites} shows the breakdown of tests. Column
``Name'' and ``Source'' show the origin of the test suite. Column
``total'' shows the number of test cases associated with a givem
source. Column ``pass-in-par.''  shows the number of test cases that
pass in their parent engine. We discarded tests that fail in their
parent engine as we could not reliably indicate the reason for the
failure, so we assumed the test could be broken. We removed
\testsThatFail{} test cases that fail for that
reason--\testsThatFailJSC{} tests from \jsc and \testsThatFailSM{}
tests from \smonkey. Column ``type-in-all'' shows the number of test
cases whose executions do not throw dynamic type errors in any of the
engines because of an undefined variable or property.  These cases
were captured by looking for the presence of \CodeIn{ReferenceError}
and \CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object).

We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. Similarly, the \chakra project does not use
  the default well-known assertions available in JS, which the other
  JS engines use.  Instead, it uses its own testing framework,
  WScript. In this case, we could not easily reproduce the \chakra
  unit tests in the other engines since it would raise a
  \texttt{ReferenceError}. Also, updating the other engines to use
  WScript would require a non-trivial manual effort. This is why
  \chakra does not appear in Table~\ref{tab:test-suites}.
  Moreover, we also did not include \hermes in the table because,
  as the reader shall see in Table~\ref{tab:test262}, \hermes presents
  a very low adherence to the Test262 conformance stuite. If we decided
  to keep \hermes, considering only the number of passing tests
  (the ``no-fail-in-all'' column), it would significantly reduce our
  amount of test files.

@@

\subsection{Mining Tests From Issue Trackers}

%o enrich our dataset of test files, we mined additional tests available on
%JavaScript GitHub projects as well as in the issue trackers of the studied
%JS engines. We explain this process next.

%\subsubsection{From GitHub projects}

%We mined JS programs from the GitHub repository. In this case, we searched
%for projects written in JavaScript, that were tagged with ``javascript-engine",
%and that have both ``Javascript" and ``engine" the name or the description of
%the project. After this process, we ended up with 2,200 JS programs, which we
%downloaded locally. However, after careful investigation, we noted that 160 of
%these projects do not have any JS file, which were excluded from our study.
%From these 2,040 projects, we could select 494,394 test files,
%which we as input to our testing approaches.

%\subsubsection{From Issue Trackers}

@@

\begin{table}[b]
  \small
  \centering
  \caption{\label{tab:cross-testing}Number of failures with
    Test Transplantation.}
  \renewcommand*{\arraystretch}{0.9}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc & \veight{} & \smonkey{} & \chakra{} \\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0
      JSC 2
      Spidermonkey 58
    }
    \jsc & - & 10 & 10 & 59 \\
    \veight{} & 41 & - & 3 & 5 \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 281 \\
    %Hermes & 8 & 14 & 8 & 26 & -  \\
    Duktape & 0 & 4 & 4 & 1 \\
    \jerry{} & 23 & 25 & 22 & 23 \\
    JSI & 0 & 0 & 0 & 0 \\
   Tiny-js & 0 & 0 & 0 & 0 \\
    \midrule
   \textbf{total} & 282 & 146 & 39 & 369  \\
    \bottomrule
  \end{tabular}
  \vspace{-3ex}
\end{table}

@@

Table~\ref{tab:cross-testing} shows the number of failures observed
for each pair of test suite and engine. The first column shows the
test suites and the first row shows the engines that run those
tests. We use a dash (``-'') to indicate that we did not consider the
combinations that associate a test suite with its parent engine.
\Fix{
In particular, we were not able to reuse the \smonkey tests on the
\hermes engine. This happened because \smonkey has its own assertion
framework, but \hermes did not interpret these assertions, resulting
in failures in all test executions from this engine. These failures
did not happen when the \smonkey tests were transplanted to the other engines,
though.
}
\Gustavo{Falar pq Hermes nao esta na tabela}
Failures in those cases would either indicate regressions or flaky
tests as opposed to unknown bugs for that engine. As explained in
Section~\ref{sec:seeds}, we used in this experiment the
\totalTestFilesForTestTransplantation{} tests included in the
rectangle area under column ``type-in-all'' from
Table~\ref{tab:test-suites}. Running those tests we observed a total
of \failuresTestTrans{} failures manifested across
\failuresTestTransDistictFiles{} distinct files
(\failuresTestTransPercent{} of total).  Table~\ref{tab:cross-testing}
shows that \smonkey\ was the engine that failed the least whereas
\chakra\ was the engine that failed the most. The \smonkey\ test suite
also revealed more failures than any other, as expected, given
that it is the suite with more tests (see
Table~\ref{tab:test-suites}).

@@

\sloppy The sources of false positives found in this experiment are as
follows:

\begin{description}
  \item[\textbf{Undefined Behavior.}] False positives of this kind are
  manifested when tests cover implementation-dependent behavior, as
  defined in the ECMA262 specification~\cite{ecmas262-spec}. For
  example, one of the tests from \jerry\ uses the function
  \CodeIn{Number.toPrecision([precision])}, which translates a number to
  a string, considering a given number of significant digits. The
  floating-point approximation of the real value is
  implementation-dependent, making that test to pass only in
  \chakra.
  \item[\textbf{Timeout/OME\footnote{ome is for out of memory
      error.}.}] False positives of this kind typically manifest when the
     engine that runs the test does not optimize the code as the original
     engine of the test. As result, the test fails to finish at the
     specified time budget or it exceeds the memory budget. For example, a
     test case from \jsc defines a function with a tail-call
     recursion. The test fails in all engines but \jsc, which implements
     tail-call optimization.

  \item[\textbf{Not implemented.}] False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} did not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}.

\item[\textbf{Non-Standard Element.}] These cases manifest when a function or
an object property is undefined in the execution engine but we were
unable to capture that by looking for error types like
\CodeIn{ReferenceError} and \CodeIn{TypeError}.\Comment{ For example,
  we found cases where the test (or its harness) fails in an assertion
  because of an undefined property.}

\item[\textbf{Other.}] This category
includes other sources of false positives. For example, it includes
the cases where the test was valid for some previous version of the
spec but is no longer valid for the current spec.

\end{description}
